Constraining the Interiors of Asteroids Through Close Encounters

### 2022-03-28 paper/main.tex
Pulled cad period and started cad speed
Made cadence period figures

In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_m$ if a uniform density distribution is assumed. We do not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is nonlinear. However, it may be a useful technique so it is mentioned here. A similar model was also studied in \jtd{Cite that paper}.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$. The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
  \label{fig:example-residuals}
\end{figure*}

@@

\jtd{Pull the correct plots from supercloud.}

>>>>

In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_m$ if a uniform density distribution is assumed. We do not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is nonlinear. However, it may be a useful technique so it is mentioned here. A similar model was also studied in Ref.~\cite{BAXANSKY2007756}.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid. The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
  \label{fig:example-residuals}
\end{figure*}

@@
